External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-11-06 CVPR2017_Review_Unified.tex
add

For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN). In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.). The models designed for AWGN would become much less effective on real noisy images.

>>>>

For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and most of them focus mainly on dealing with additive white Gaussian noise (AWGN). In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.). The models designed for AWGN would become much less effective on real noisy images.
